---
title: "Word Cloud"
author: "Cali Pfleger"
date: "2/21/2021"
output: 
  html_document:
    code_folding: hide
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lipdR)
library(geoChronR)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(magrittr)
library(patchwork)
library(RColorBrewer)
library(tidyr)
library(ggplot2)
library(gganimate)
library(hrbrthemes)
library(packcircles)
library(viridis)
library(ggiraph)
library(ggbernie)
library(fmsb)
library(viridis)
library(hrbrthemes)
library(igraph)
library(ggraph)
library(colormap)
library(tm)
library(SnowballC)
library(wordcloud)
library(dplyr)
library(janitor)
library(stringr)
library(here)
library(tidyverse)
library(tidytext)
library(textdata)
library(pdftools)
library(ggwordcloud)
```

## Data Citation

Konecky, Bronwen L., et al. “The Iso2k Database: a Global Compilation  of Paleo-δ18O and δ2H Records to Aid  Understanding of Common Era Climate.” Earth System Science Data, vol. 12, no. 3, 2020, pp. 2261–2288., doi:10.5194/essd-12-2261-2020. 

## Import text 
```{r, warning=FALSE, message=FALSE, include=FALSE}
iso <- readLipd("http://lipdverse.org/iso2k/1_0_0/iso2k1_0_0.zip")
```

## Wrangle Data
```{r}
TS <- extractTs(iso)
tTS <- tidyTs(TS,age.var = "year") 
```

## Filter Data to Get the Primary Timeseries
```{r}
iTS <-  filter(tTS, paleoData_iso2kPrimaryTimeseries == TRUE) 
```

## Get the Word Cloud Set and Write CSV
```{r, warning=FALSE, message=FALSE}
word_cloud_set <-  iTS %>% 
  select(archiveType, geo_siteName, interpretation1_inferredMaterial, interpretation1_variable, interpretation1_variableGroup, interpretation2_inferredMaterial, interpretation2_variable, interpretation2_variableGroup, paleoData_description, paleoData_TSid, paleoData_values, paleoData_variableName, year, paleoData_inferredMaterialGroup)  

word_cloud <- as.data.frame(word_cloud_set)

##
write_csv(word_cloud, path = here("data", "word_cloud.csv"), col_names = T)
```

## Wrtie Iso2k CSV 
```{r, warning=FALSE, message=FALSE, include=FALSE}
iso2k <- readr::read_csv(here("data", "word_cloud.csv"))

remove_all_ws<- function(string){
    return(gsub(" ", "", str_squish(string)))
}
```

## Wrangle Iso2k Data for Word Cloud 
```{r, warning=FALSE, message=FALSE, include=FALSE}
iso2k_archiveType<-iso2k %>%
  select(archiveType) %>% 
  clean_names() %>% 
  mutate_if(is.character, remove_all_ws)
#  case_when(country %in% c("UnitedStatesofAmerica") ~ "USA")

docs <- Corpus(VectorSource(iso2k_archiveType))

inspect(docs)

toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")

docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("unbranded", "null")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)

dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)
```

## Iso2k Primary Timeseries Wordcloud
```{r, warning=FALSE, message=FALSE}

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=1000, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```


## Read in Iso2k Paper as .pdf 
```{r, cache = TRUE}
iso_text <- pdf_text("iso2k.pdf")
```

## Wrangle Iso2k Paper and Perform Sentiment Analysis
```{r, warning=FALSE, message=FALSE}
iso_tidy <- data.frame(iso_text) %>% 
  mutate(text_full = str_split(iso_text, pattern = '\\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full))  %>% 
  unnest_tokens(word, text_full)  %>% 
  anti_join(stop_words) %>% 
  count(word) 

iso_bing <- iso_tidy%>% 
  inner_join(get_sentiments("bing"))  

iso_nrc <- iso_tidy%>% 
  inner_join(get_sentiments("nrc"))%>% 
  group_by(word, sentiment)

iso_combo <- iso_bing %>% 
  inner_join(get_sentiments("nrc"))
  
```

## Vizualizatoin of Sentiment 
```{r}
ggplot(data = iso_combo, aes(y = word, x = n)) +
  geom_col() + 
  facet_wrap(~sentiment) + 
  labs(title=paste("Senitment of Iso2k Database")) +
  xlab("Counts") +
  ylab("Word") +
theme(axis.text.y = element_text(size = 4.5)) 
```